---
title: "LISI 3 gasses 3 acq each"
author: "Davidheiser"
date: "Aug 2019"
output: html_document
---

Code version: updated July 2019

MANUALLY UPDATE: user defined, session-specific information
```{r manual-definitions}
User <- "Brett"
session <-"LISI 3 gases" 
MS.ID<-"Bert"   #don't change this unless we get a new mass spec or you are using this for data from another lab :)   

```

## Install custom packages
These will change frequently over the next couple of years, so it is wise to reinstall them everytime, to be sure you are using the up-to-date versions of the functions that the code below needs. If there haven't been any changes to the codes, it will say that and not reinstall them.
```{r install, eval = FALSE}
#devtools::install_github("KopfLab/isoreader")

#devtools::install_github("cubessil/isoprocessCUBES") #general CUBESsil lab stuff

#devtools::install_github("cubessil/CUBESSILclumpedmath") #only for processing clumped data

#devtools::install_github("cubessil/clumpsDRcodes") #only for processing clumped data

```

## Load libraries and clumped isotope standard values

```{r message = FALSE, warning = FALSE}
library(rlang)
library(plotly)
library(isoreader)
library(tidyverse)
library(minpack.lm)
library(CUBESSILclumpedmath)
```

## Load all did files in a folder (or multiple folders)

Catches any errors and exceptions that might occur and reports them as "problems".
```{r load-data}
readrawdata <-T
if (readrawdata){
folder <- file.path("one side MV","190812_Brett test LISI oneside4")
  stopifnot(file.exists(folder))
  tictoc::tic()
  did_files <- iso_read_dual_inlet(folder,cache = TRUE, quiet = FALSE, read_vendor_data_table = FALSE, parallel = TRUE)
  tictoc::toc()
  did_files <- iso_filter_files_with_problems(did_files)  
  saveRDS(did_files, paste0(session, "_did_files.RDS"))
}else{
  did_files <- readRDS(paste0(session, "_did_files.RDS"))
}

  rawdata <- did_files %>% iso_get_raw_data(include_file_info = c(Analysis, file_datetime, Preparation, `Identifier 1`, `Identifier 2`, MS_integration_time.s, Method, measurement_info))
 
```
##This file is run with 5sec int and 150 cyc with largist to normal size sample. 
```{r}
samplegasside <- rawdata %>% filter(type=="sample") %>%
  mutate( r45o44 = v45.mV / v44.mV,
          r46o44 = v46.mV / v44.mV,  
          r47o44 = v47.mV / v44.mV,  
          r48o44 = v48.mV / v44.mV,  
          r49o44 = v49.mV / v44.mV,
          logr45o44 = log(v45.mV)- log(v44.mV),
          logr46o44 = log(v46.mV)- log(v44.mV),
          logr47o44 = log(v47.mV)- log(v44.mV),  
          logr48o44 = log(v48.mV)- log(v44.mV)
          ) 
samplegasside %>% select(-measurement_info) %>%  write.csv( "rawdata.csv")
```

```{r group samples}
samplegasside<- samplegasside%>% arrange(Analysis) %>% 
  mutate(
      new_sample =  Analysis != c("", head(Analysis, -1)),
      batch = cumsum(new_sample)) 
```

```{r Analysisvs45o44 plot}
Analysisvs45o44 <- samplegasside %>% 
  ggplot(aes(x=batch, y=logr45o44)) + 
  geom_boxplot()+
  geom_point(aes(color=v44.mV, shape=`Identifier 1`))
ggplotly(Analysisvs45o44)
```
##
```{r v44mVvs45o44}
v44.mVvs45o44 <- samplegasside %>% 
  ggplot() + 
  geom_point(aes(x=v44.mV, y=r45o44, color= file_datetime))
ggplotly(v44.mVvs45o44)
```
```{r 47}
v44.mVvs47o44 <- samplegasside %>% filter(`Identifier 1`=="Yellowstone") %>% 
  ggplot(aes(x=v44.mV, y=r47o44, shape=Analysis, color=file_datetime)) + 
  geom_point()+
  stat_smooth(method = "gam", formula = y ~ s(x, k = 3), size = 1)
  #stat_smooth(method = "lm", formula = y ~ x + I(x^2), size = 1,color="red")
ggplotly(v44.mVvs47o44)
```



```{r 47 group}
v44.mVvs47o44groupof5 <- samplegasside %>% filter(`Identifier 1`=="Yellowstone") %>% 
  ggplot(aes(x=v44.mV, y=r47o44, shape=as.character(batch), color=file_datetime)) + 
  #geom_point()+
  stat_smooth(method = "gam", formula = y ~ s(x, k = 3), size = 1)
  #stat_smooth(method = "lm", formula = y ~ x + I(x^2), size = 1,color="red")
ggplotly(v44.mVvs47o44groupof5)
```
```{r}
samplegasside %>% select( -measurement_info) %>%  write.csv("samplegasside.csv")

```

```{r, this can't be right}

JohnsonandPoissonNoise <- function(mV,R, integrationTime){
  kB = 1.38064852*10^-23 #Boltzman's constant
  T = 290 # Kelvin
  R = 1E11  # resistor size
  amplifierNoiseVariance = 4*kB*T*R  #Johnson-Nyquist noise

  cpsPerVolt = 6.24150934*10^18/R  # elementary charge, Ohm's Law
  
  noiseVariance= ((mV*1000)/cpsPerVolt + amplifierNoiseVariance) / integrationTime 
  noiseVariance
}
```

kB = 1.38064852*10^-23 #Boltzman's constant
T = 290 # Kelvin
R = 1E11  # resistor size
amplifierNoiseVariance = 4*kB*T*R  #Johnson-Nyquist noise

cpsPerVolt = 6.24150934*10^18/R;  % elementary charge, Ohm's Law

```{r mixing resistor in this mutate call}
samplegasside<- samplegasside %>%  
    mutate(
            simDNoisy_v44.mV = JohnsonandPoissonNoise(v44.mV, 10^8,5),
            simDNoisy_v45.mV = JohnsonandPoissonNoise(v45.mV, 10^10,5),
            simDNoisy_v46.mV = JohnsonandPoissonNoise(v46.mV, 10^11,5),
            simDNoisy_v47.mV = JohnsonandPoissonNoise(v47.mV, 10^13,5),
            simDNoisy_v48.mV = JohnsonandPoissonNoise(v48.mV, 10^13,5),
            simDNoisy_v49.mV = JohnsonandPoissonNoise(abs(v49.mV), 10^13,5))

getPred <- function(parS, xx) parS$a * exp(xx * parS$b) + parS$c 
## residual function 
residFun <- function(p, observed, xx) observed - getPred(p,xx)
## starting par
parStart <- list(a=3,b=-.01, c=-35)


tictoc::tic()
r45o44_fit <- nls.lm(par=parStart, fn = residFun, observed = samplegasside$simDNoisy_v45.mV, xx = samplegasside$r45o44, control = nls.lm.control(nprint=0, maxiter = 150))
r46o44_fit <- nls.lm(par=parStart, fn = residFun, observed = samplegasside$simDNoisy_v46.mV, xx = samplegasside$r46o44, control = nls.lm.control(nprint=0, maxiter = 150))
tictoc::toc()

```

```{r}
# 
samplegasside_long_ratios <- samplegasside %>% 
  gather(key = "ratio_name", value = "ratio_value", matches("^r\\d{2}o\\d{2}"))
samplegasside_long_ratios_log <- samplegasside %>% 
  gather(key = "ratio_name", value = "ratio_value", matches("^logr\\d{2}o\\d{2}"))

# available standards data
standards <- filter(samplegasside_long_ratios, `Identifier 1` == "Yellowstone")
standardslog <- filter(samplegasside_long_ratios_log, `Identifier 1` == "Yellowstone")

# prepare sample data frame
find_std_analyses_by_time_range <- function(sample_data, std_data, time_range) {
  date_range <- range(sample_data$file_datetime)
  date_range <- c(date_range[1] - time_range, date_range[2] + time_range)
  dplyr::filter(std_data, dplyr::between(file_datetime, !!date_range[1], !!date_range[2])) %>% 
    dplyr::pull(Analysis) %>% unique()
}
pull_std_data_by_analyses_and_ratio <- function(analyses, ratio_name, std_data) {
  dplyr::filter(std_data, Analysis %in% !!analyses, ratio_name == !!ratio_name) %>% 
    select(ratio_name, ratio_value, v44.mV)
}
samples <- samplegasside_long_ratios %>% 
  nest(-Analysis, -ratio_name, .key = "sample_data") %>% 
  # generate calibration data structure
  mutate(
    std_analyses = map(
      .x = sample_data, 
      .f = find_std_analyses_by_time_range, 
      # constants
      std_data = standards, 
      time_range = lubridate::duration(1, "hours")),
    std_data = map2(
      .x = std_analyses,
      .y = ratio_name,
      .f = pull_std_data_by_analyses_and_ratio,
      # constants
      std_data = standards
    )
  ) %>% 
  arrange(Analysis, ratio_name)
stopifnot(all(map_int(samples$std_analyses, length) > 0))
# generate fits
generate_std_fit <- function(std_data) {
  stats::glm(ratio_value ~ v44.mV, data = std_data)
  #add exp here
}

apply_std_fit <- function(sample_data, std_fit) {
  
  std_fit_predict <- predict(std_fit, newdata = select(sample_data, v44.mV), se.fit = TRUE)
  
  mutate(sample_data,
         std_ratio_value = std_fit_predict$fit,
         std_ratio_se = std_fit_predict$se.fit
  )
}
samples_with_fit <- 
  samples %>% 
  # apply calibration
  mutate(
    std_fit = map(
      .x = std_data, 
      .f = generate_std_fit
    ),
    fit_summary = map(std_fit, broom::glance),
    sample_data = map2(
      .x = sample_data,
      .y = std_fit,
      .f = apply_std_fit
    ) 
  )

```
```{r playing}
unnestestedfit <- unnest(samples_with_fit, sample_data, fit_summary)
unnestestedfit %>% ggplot()+
  aes(x = v44.mV) +
  geom_point( aes(x= `deviance`, y = null.deviance, color= file_datetime))
unnestestedfit %>% ggplot()+
  aes(x = v44.mV) +
  geom_point( aes(x= `deviance`, y = BIC, color= file_datetime))    
  
  

unnestestedfit %>% mutate(
  dx= ratio_value/std_ratio_value
) %>% select(dx,everything()) %>% filter(`Identifier 1`!="Yellowstone")

write.csv(select(unnestestedfit, -measurement_info, -std_data, -std_fit, -std_analyses), "samples_with_fit.csv")
```


# ```{r}
# # take a look
# samples_with_fit %>% 
#   ggplot() + 
#   aes(x = v44.mV) +
#   geom_point(
#     data = function(df) unnest(df, sample_data) %>% mutate(panel = "sample_data"),
#     mapping = aes(y = ratio_value, color = `Identifier 1`, shape = panel)
#   ) +
#   # geom_point(
#   #   data = function(df) unnest(df, std_data) %>% mutate(panel = "standard data"),
#   #   mapping = aes(y = ratio_value, shape = panel), 
#   #   alpha = 0.5
#   # ) +
#   # error bar for pressure matched
#   geom_errorbar(
#     data = function(df) unnest(df, sample_data) %>% mutate(panel = "pressure matched standard estimate"),
#     mapping = aes(ymin = std_ratio_value - std_ratio_se, ymax = std_ratio_value + std_ratio_se),
#     width = 0
#   ) +
#   geom_point(
#     data = function(df) unnest(df, sample_data) %>% mutate(panel = "pressure matched standard estimate"),
#     mapping = aes(y = std_ratio_value, shape = panel)
#   ) +
#   facet_grid(ratio_name ~ panel, scales = "free")
# ggplotly()
# ```

# ```{r}
# samples_with_fit %>% unnest(sample_data) %>% filter(Analysis %in% c(34851)) %>% 
#     ggplot(aes(x=std_ratio_value, y=v44.mV,color=`Identifier 1`))+
#         geom_point()+
#         facet_grid(ratio_name ~ `Identifier 1`, scales = "free")
# ggplotly()
# 
# samples_with_fit %>% unnest(sample_data) %>% filter(Analysis %in% c(34851)) %>% filter(ratio_name =="r47o44") %>% 
#     ggplot(aes(x=std_ratio_value, y=ratio_value,color=`v44.mV`))+
#         geom_point()
#         
# 
# samplegasside %>% filter(Analysis %in% c(34851)) %>% select("r47o44") %>% 
#   summarise(mean(r47o44),
#             sd(r47o44))
# 
# samples_with_fit %>% unnest(sample_data) %>% filter(Analysis %in% c(34851)) %>% filter(ratio_name =="r47o44") %>% 
#   summarise(mean(std_ratio_value),
#             sd(std_ratio_value),
#             mean(ratio_value),
#             sd(ratio_value)
#             )
# ```



```{r}
samplegasside_long_ratios_withfit <- samples_with_fit %>% unnest(sample_data) %>% 
            filter(Analysis==34842 & cycle %in% c(1:150))  %>% group_by(cycle) %>% #& cycle %in% c(1,2,3,4,5,6,7,8)
            spread(ratio_name,ratio_value,sep = "_") %>% summarise_all(funs(ifelse(is.numeric(.),mean(.,na.rm=T),.)))
samplegasside_long_ratios_withfit

flatlistdata.fit <- samplegasside_long_ratios_withfit %>% mutate( Donotuse="",
                                              runinfo="") %>% clumpedbyCyc_withfit


D47 <- flatlistdata.fit %>% 
  filter(Donotuse != TRUE) %>%
  ggplot() + 
  geom_point(aes(x=d47, y=D47full))
D47v44mV <- flatlistdata.fit %>% 
  filter(Donotuse != TRUE) %>%
  ggplot() + 
  geom_point(aes(x=v44.mV, y=D47full))
subplot(D47,D47v44mV)

```

```{r normal vs fit d18O d13C}
flatlistbycyc <- clumpedbyCyc(rawdata)


d18Od13Cfit <- flatlistdata.fit %>% 
  filter(Donotuse != TRUE) %>%
  ggplot() + 
  geom_point(aes(x=d18O, y=d13C))
d18Od13Cnormal <- flatlistbycyc %>% filter(Analysis>34842 &Analysis<34843 ) %>% 
  filter(Donotuse != TRUE) %>%
  ggplot() + 
  geom_point(aes(x=d18O, y=d13C))
subplot(d18Od13Cfit,d18Od13Cnormal)

```

```{r normal vs fit clumped}

D47fit <- flatlistdata.fit %>% 
  filter(Donotuse != TRUE) %>%
  ggplot() + 
  geom_point(aes(x=d47, y=D47full))
D47normal <- flatlistbycyc %>% filter(Analysis>34842 &Analysis<34843 ) %>% 
  filter(Donotuse != TRUE) %>%
  ggplot() + 
  geom_point(aes(x=d47, y=D47full))
subplot(D47fit,D47normal)


flatlistbycyc %>% filter(Analysis>34842 &Analysis<34843 ) %>% select(d47)
flatlistdata.fit %>% select(d47,ratio_name_r47o44,std_ratio_value)
```



```{r}
library(dplyr)
df <- data.frame(x = c(NA, "a.b", "a.d", "b.c"))
df %>% separate(x, c("A", "B"))

# If you just want the second variable:
df %>% separate(x, c(NA, "B"))
```

```{r}
library(dplyr)
stocks <- data.frame(
  time = as.Date('2009-01-01') + 0:9,
  X = rnorm(10, 0, 1),
  Y = rnorm(10, 0, 2),
  Z = rnorm(10, 0, 4)
)
stocksm <- stocks %>% gather(stock, price, -time)
stocksm %>% spread(stock, price)
stocksm %>% spread(time, price)
```

```{r}

```


```{r}
##### example 2 

## function to simulate data 
f <- function(TT, tau, N0, a, f0) {
    expr <- expression(N0*exp(-TT/tau)*(1 + a*cos(f0*TT)))
    eval(expr)
}

## helper function for an analytical gradient 
j <- function(TT, tau, N0, a, f0) {
    expr <- expression(N0*exp(-TT/tau)*(1 + a*cos(f0*TT)))
    c(eval(D(expr, "tau")), eval(D(expr, "N0" )),
      eval(D(expr, "a"  )), eval(D(expr, "f0" )))
}

## values over which to simulate data 
#TT <- samplegasside %>% filter(Analysis== 34848) %>% select(v44.mV) 
#TT <- TT$v44.mV
TT <- seq(0, 8, length=501)

## parameter values underlying simulated data  
p <- c(tau = 2.2, N0 = 1000, a = 0.25, f0 = 8)

## get data 
Ndet <- do.call("f", c(list(TT = TT), as.list(p)))
## with noise
N <- Ndet +  rnorm(length(Ndet), mean=Ndet, sd=.01*max(Ndet))

## plot the data to fit
par(mfrow=c(2,1), mar = c(3,5,2,1))  
plot(TT, N, bg = "black", cex = 0.5, main="data")

## define a residual function 
fcn     <- function(p, TT, N, fcall, jcall)
    (N - do.call("fcall", c(list(TT = TT), as.list(p))))

## define analytical expression for the gradient 
fcn.jac <- function(p, TT, N, fcall, jcall) 
    -do.call("jcall", c(list(TT = TT), as.list(p)))

## starting values 
guess <- c(tau = 2.2, N0 = 1500, a = 0.25, f0 = 10)

## to use an analytical expression for the gradient found in fcn.jac
## uncomment jac = fcn.jac
out <- nls.lm(par = guess, fn = fcn, jac = fcn.jac,
              fcall = f, jcall = j,
              TT = TT, N = N, control = nls.lm.control(nprint=1))

## get the fitted values 
N1 <- do.call("f", c(list(TT = TT), out$par))   

## add a blue line representing the fitting values to the plot of data 
lines(TT, N1, col="blue", lwd=2)

## add a plot of the log residual sum of squares as it is made to
## decrease each iteration; note that the RSS at the starting parameter
## values is also stored
plot(1:(out$niter+1), log(out$rsstrace), type="b",
main="log residual sum of squares vs. iteration number",
xlab="iteration", ylab="log residual sum of squares", pch=21,bg=2) 

## get information regarding standard errors
summary(out) 

```


